Debugging of RxJS-based Applications

### 2020-08-20 paper.tex
Switch to acmart

\documentclass[12pt,a4paper]{article}
\usepackage{ccicons}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{graphicx}
\usepackage{booktabs}

\usepackage{./tikzit}

@@

\newcommand{\version}{v0.12}

\begin{document}
\begin{centering}

	\Large{Workshop Paper}
	\par
	\Huge{Debugging of RxJS-based Applications}
	\par
	\vspace{2ex}

	\normalsize{
		Manuel Alabor\\
		Supervised by Prof. Dr. Markus Stolze\\
		\par
		\vspace{2ex}
		HSR University of Applied Sciences Rapperswil, Switzerland\\
		\par
		\vspace{2ex}
		\today{} (\version)
	}
	\par
	\vspace{2ex}

	\begin{quotation}
		\small{
			\noindent\textbf{Abstract}---\input{./abstract.tex}
		}
		\par
		\vspace{4ex}
	\end{quotation}
\end{centering}

@@

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[node distance = 5.5cm, auto]
		\tikzstyle{block} = [rectangle, draw,
		text width=5em, text centered, rounded corners, minimum height=2.5em]

@@

		\draw [<->] (user) to node {Interaction} (ui);
		\draw [->] (ui.north) to[bend left=20] node {Interaction Data Flow} (system.north);
		\draw [->] (system.south) to[bend left=20] node {Update Data Flow} (ui.south);
	\end{tikzpicture}
	\caption{Basic Dataflows in a UI Application.}
	\label{fig:ui-data-flows}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\tikzfig{debugging-process-model}
	\caption{Debugging Process Model after Layman et al. \cite{Layman_Diep_Nagappan_Singer_Deline_Venolia_2013}}
	\label{fig:debugging-process-model}
\end{figure}

@@

		of(0, 1, 2, 3, 4).pipe(	// Create Observable with Integers
			filter(i => i < 4),		// Omit Integers >= 4
			map(i => i * 2)				// Multiply Integer with 2
		).subscribe(console.log) // Emits 0, 2, 4, 6
	\end{minted}
	\caption{Basic RxJS example creating an Observable emitting four integers. Each integer is processed by two operators and finally written to the console.}
	\label{lst:rp-with-rxjs}
\end{listing}

@@

\begin{figure}[H]
	\centering
	\tikzfig{marble-diagram}
	\caption{A Marble Diagram visualizing the Observable in Listing~\ref{lst:rp-with-rxjs}. From left to right, each marble represents an emitted value. The vertical line at the last marble indicates that the Observable completed after emitting \mintinline{TypeScript}{6}.}
	\label{fig:marble-diagram}
\end{figure}

@@

\begin{table}[H]
	\begin{tabular}{ p{0.2\linewidth}  p{0.225\linewidth}  p{0.225\linewidth} p{0.225\linewidth} }
		\toprule
		\textbf{Subject} & \textbf{Trace Logs} & \textbf{Debugger} & \textbf{Add. Tools} \\ \midrule
		\textbf{S1}      & \small{X}           &                   &                     \\ \midrule
		\textbf{S2}      & \small{X}           & \small{X}         &                     \\ \midrule
		\textbf{S3}      & \small{X}           &                   &                     \\ \midrule
		\textbf{S4}      & \small{X}           & \small{X}         & \small{Next step}   \\ \bottomrule
	\end{tabular}
	\caption{Observed practices and tool usage per subject.}
	\label{tab:subject-techniques}
\end{table}

@@

\begin{table}[H]
	\begin{tabular}{ p{0.2\linewidth}  p{0.355\linewidth}  p{0.355\linewidth} }
		\toprule
		\textbf{Subject} & \textbf{Problem 1} & \textbf{Problem 2} \\ \midrule
		\textbf{S1}      & \small{Time expired}       & \small{Time expired}     \\ \midrule
		\textbf{S2}      & \small{Time expired}       & \small{Time expired}     \\ \midrule
		\textbf{S3}      & \small{Time expired}       & \small{Time expired}     \\ \midrule
		\textbf{S4}      & \small{Solved}             & \small{Time expired}     \\ \bottomrule
		\end{tabular}
	\caption{Results per subject for each presented problem.}
	\label{tab:subject-results}
\end{table}

@@

\begin{table}[H]
	\begin{tabular}{ p{0.13\linewidth}  p{0.08\linewidth}  p{0.12\linewidth} p{0.23\linewidth} p{0.28\linewidth}}
		\toprule
		\textbf{Subject} & \textbf{Q1} & \textbf{Q2}         & \textbf{Q3}               & \textbf{Q4}                             \\ \midrule
		\textbf{S1}      & \small{Yes} & \small{1 year}      & \small{Frontend}          & \small{Trace Logs, rxjs-spy}            \\ \midrule
		\textbf{S2}      & \small{No}  & \small{$>$ 3 years} & \small{Frontend}          & \small{Debugger, Trace Logs}            \\ \midrule
		\textbf{S3}      & \small{Yes} & \small{2 years}     & \small{Frontend}          & \small{Debugger, Trace Logs, rxjs-spy}  \\ \midrule
		\textbf{S4}      & \small{No}  & \small{2 years}     & \small{Frontend, Backend} & \small{Debugger, Trace Logs}            \\ \bottomrule
	\end{tabular}
	\caption{After-action survey responses per subject.}
	\label{tab:subject-survey}
\end{table}

@@

As of writing this paper, the projects owner stopped working actively on the open source application and is looking for a new maintainer\cite{rxviz-maintainer}.

@@

\bibliographystyle{splncs04}
\bibliography{bibliography.bib}

\section*{License}
\ccby\thinspace\thinspace This work is licensed under a \href{https://creativecommons.org/licenses/by/4.0/}{Creative Commons Attribution 4.0 International License}.
\end{document}

>>>>

\documentclass[sigplan,screen,review]{acmart}
\usepackage{ccicons}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{./tikzit}

@@

% Top Matter: https://mirror.kumi.systems/ctan/macros/latex/contrib/acmart/acmart.pdf
\acmConference[SPLASH '20]{SPLASH '20: 7th Workshop on Reactive and Event-based Languages \& Systems}{November 15--20, 2020}{Chicago}
\title{Debugging of RxJS-based Applications}
\author{Manuel Alabor}
\affiliation{
	\institution{HSR University of Applied Sciences}
	\city{Rapperswil}
	\country{Switzerland}
}
\email{malabor@hsr.ch}

\begin{document}

\begin{abstract}
	\input{./abstract.tex}
\end{abstract}

\begin{CCSXML}
	<ccs2012>
	   <concept>
		   <concept_id>10011007</concept_id>
		   <concept_desc>Software and its engineering</concept_desc>
		   <concept_significance>500</concept_significance>
		   </concept>
	 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering}

\keywords{reactive programming, debugging, empirical software engineering}

\maketitle

@@

\begin{figure}
	\centering
	\begin{tikzpicture}[node distance = 5.5cm, auto]
		\tikzstyle{block} = [rectangle, draw,
		text width=5em, text centered, rounded corners, minimum height=2.5em]

@@

		\draw [<->] (user) to node {Interaction} (ui);
		\draw [->] (ui.north) to[bend left=20] node {Interaction Data Flow} (system.north);
		\draw [->] (system.south) to[bend left=20] node {Update Data Flow} (ui.south);
	\end{tikzpicture}
	\Description{Basic Dataflows in a UI Application.}
	\caption{Basic Dataflows in a UI Application.}
	\label{fig:ui-data-flows}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\tikzfig{debugging-process-model}
	\Description{Debugging Process Model after Layman et al. \cite{Layman_Diep_Nagappan_Singer_Deline_Venolia_2013}}
	\caption{Debugging Process Model after Layman et al. \cite{Layman_Diep_Nagappan_Singer_Deline_Venolia_2013}}
	\label{fig:debugging-process-model}
\end{figure}

@@

		of(0, 1, 2, 3, 4).pipe(	// Create Observable with Integers
			filter(i => i < 4),		// Omit Integers >= 4
			map(i => i * 2)				// Multiply Integer with 2
		).subscribe(console.log) // Emits 0, 2, 4, 6
	\end{minted}
	\Description{Basic RxJS example creating an Observable emitting four integers. Each integer is processed by two operators and finally written to the console.}
	\caption{Basic RxJS example creating an Observable emitting four integers. Each integer is processed by two operators and finally written to the console.}
	\label{lst:rp-with-rxjs}
\end{listing}

@@

\begin{figure}[H]
	\centering
	\tikzfig{marble-diagram}
	\Description{A Marble Diagram visualizing the Observable in Listing~\ref{lst:rp-with-rxjs}. From left to right, each marble represents an emitted value of 0, 2, 4, and 6. The vertical line at the last marble indicates that the Observable completed after emitting value \mintinline{TypeScript}{6}.}
	\caption{A Marble Diagram visualizing the Observable in Listing~\ref{lst:rp-with-rxjs}. From left to right, each marble represents an emitted value. The vertical line at the last marble indicates that the Observable completed after emitting \mintinline{TypeScript}{6}.}
	\label{fig:marble-diagram}
\end{figure}

@@

\begin{table}
	\begin{tabular}{ p{0.2\linewidth}  p{0.225\linewidth}  p{0.225\linewidth} p{0.225\linewidth} }
		\toprule
		\textbf{Subject} & \textbf{Trace Logs} & \textbf{Debugger} & \textbf{Add. Tools} \\ \midrule
		\textbf{S1}      & \small{X}           &                   &                     \\ \midrule
		\textbf{S2}      & \small{X}           & \small{X}         &                     \\ \midrule
		\textbf{S3}      & \small{X}           &                   &                     \\ \midrule
		\textbf{S4}      & \small{X}           & \small{X}         & \small{Next step}   \\ \bottomrule
	\end{tabular}
	\caption{Observed practices and tool usage per subject.}
	\label{tab:subject-techniques}
\end{table}

@@

\begin{table}
	\begin{tabular}{ p{0.2\linewidth}  p{0.355\linewidth}  p{0.355\linewidth} }
		\toprule
		\textbf{Subject} & \textbf{Problem 1} & \textbf{Problem 2} \\ \midrule
		\textbf{S1}      & \small{Time expired}       & \small{Time expired}     \\ \midrule
		\textbf{S2}      & \small{Time expired}       & \small{Time expired}     \\ \midrule
		\textbf{S3}      & \small{Time expired}       & \small{Time expired}     \\ \midrule
		\textbf{S4}      & \small{Solved}             & \small{Time expired}     \\ \bottomrule
	\end{tabular}
	\caption{Results per subject for each presented problem.}
	\label{tab:subject-results}
\end{table}

@@

\begin{table}
	\begin{tabular}{ p{0.13\linewidth}  p{0.08\linewidth}  p{0.12\linewidth} p{0.23\linewidth} p{0.28\linewidth}}
		\toprule
		\textbf{Subject} & \textbf{Q1} & \textbf{Q2}         & \textbf{Q3}               & \textbf{Q4}                             \\ \midrule
		\textbf{S1}      & \small{Yes} & \small{1 year}      & \small{Frontend}          & \small{Trace Logs, rxjs-spy}            \\ \midrule
		\textbf{S2}      & \small{No}  & \small{$>$ 3 years} & \small{Frontend}          & \small{Debugger, Trace Logs}            \\ \midrule
		\textbf{S3}      & \small{Yes} & \small{2 years}     & \small{Frontend}          & \small{Debugger, Trace Logs, rxjs-spy}  \\ \midrule
		\textbf{S4}      & \small{No}  & \small{2 years}     & \small{Frontend, Backend} & \small{Debugger, Trace Logs}            \\ \bottomrule
	\end{tabular}
	\caption{After-action survey responses per subject.}
	\label{tab:subject-survey}
\end{table}

@@

@@

\begin{acks}
	We would like to
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

\end{document}
